### 2016-07-13 Docs/managing_jobs/managingjobs.tex
add a note about gfortra 6.1.1 compiler bug

\begin{itemize}
\item {\em gfortran 4.5.x}: gfortran 4.5 has no known issues.

\item {\em gfortran 4.6.x}: gfortran 4.6.1--4.6.3 on Fedora 
(15 and 16) have a bug that shows up in multi-processor, multilevel
runs ({\tt toy\_convect} on 4 processors, with {\tt
inputs\_2d\_ml.test} for instance).  The symptom is a crash during
initialization with the message that ``message sizes do not match
across processes in the collective'' in a {\tt parallel\_bcast} call.
This is in {\tt cluster\_f.f90}, and the issue seems to be a
multiplication error in computing the size to allocate {\tt bxs}.  The
bug is not present when you compile in debug mode, so it seems to be
related to optimization.

\item {\em gfortran 4.7.x}: gfortran 4.7.1 (prerelease) seems to have 
fixed the above issue, but now wdconvect with 2-level, effective
768$^3$ dies due to an unknown seg fault at the beginning of the run.

@@

@@

>>>>

\begin{itemize}

@@

gfortran 4.8.5 appears to work without issues

@@

\item {\em gfortran 6.1.1}: These compilers have a bug in producing
  optimized code for \boxlib's {\tt init\_layout\_tilearray}.  At the
  moment, this is worked around in \boxlib\ by changing the routine
  from a function to a subroutine.
